Do NBA Teams Avoid Trading within Their Own Division?

### 2022-05-10 Manuscript.Rmd
Set the date to May 5 2022

---
title: "Do NBA Teams Avoid Trading within Their Own Division?"
author: 
  - first_name: jimi
    last_name: adams
    orcid_id: "0000-0001-5043-1149"
    affiliation: University of Colorado Denver, USA
  - first_name: Michał
    last_name: Bojanowski
    orcid_id: "0000-0001-7503-852X"
    affiliation: Kozminski University, Warsaw, Poland
date: "November 29, 2021"
description: "Within US professional sports, trades within one's own division are often perceived to be disadvantageous. We ask how common this practice is. To examine this question, we construct a date-stamped network of all trades in the NBA between June 1976 and May 2019. We then use yearly weighted exponential random graph models to estimate the likelihood of teams avoiding within-division trade partners, and whether that pattern changes through time. In addition to the empirical question, this analysis serves to demonstrate the necessity and difficulty of constructing the proper baseline for statistical comparison. We find limited-to-no support for the popular perception.<br/><br/>**Draft under review**."
output: 
  distill::distill_article:
    toc: true
    code_folding: false
    keep_md: true
link-citations: true
repository_url: https://github.com/mbojan/nba-trades
bibliography: nba_trades.bib
---

>>>>

---
title: "Do NBA Teams Avoid Trading within Their Own Division?"
author: 
  - first_name: jimi
    last_name: adams
    orcid_id: "0000-0001-5043-1149"
    affiliation: University of Colorado Denver, USA
  - first_name: Michał
    last_name: Bojanowski
    orcid_id: "0000-0001-7503-852X"
    affiliation: Kozminski University, Warsaw, Poland
date: "May 10, 2022"
description: "Within US professional sports, trades within one's own division are often perceived to be disadvantageous. We ask how common this practice is. To examine this question, we construct a date-stamped network of all trades in the NBA between June 1976 and May 2019. We then use yearly weighted exponential random graph models to estimate the likelihood of teams avoiding within-division trade partners, and whether that pattern changes through time. In addition to the empirical question, this analysis serves to demonstrate the necessity and difficulty of constructing the proper baseline for statistical comparison. We find limited-to-no support for the popular perception.<br/><br/>**Draft under review**."
output: 
  distill::distill_article:
    toc: true
    code_folding: false
    keep_md: true
link-citations: true
repository_url: https://github.com/mbojan/nba-trades
bibliography: nba_trades.bib
---
